Simulataneous Robot Localization and \\Environment Mapping with \\Simulated Sensor Measurements

### 2018-05-03 paper.tex
Added maths

%---------------------------------
% Manually-included packages
\usepackage{graphicx}

@@

Once these measurements are collected, the \texttt{EKFSlammer} class is instantiated. This class 
represents the robot's predicted measurements by the Extended Kalman Filter. It also represents 
the EKF's entire algorithmic complexity. The a priori and the a posteriori estimation steps are 
performed through several of the \texttt{EKFSlammer}'s class methods.

@@

First, to generate the a priori estimate, the \texttt{motionModelUpdate()} method is called by 
\texttt{ekfUpdate}. Its parameters are the timestep for the robot and its control parameters, in 
the form of a forward velocity and an angular velocity (i.e. the \texttt{controlIn} struct; see 
\texttt{Utils.h}). The \texttt{motionModelUpdate} will recalculate the estimated state of the 
robot, given the control input and given the known uncertainties of the robot's actuators 
(i.e. the robot's wheels, since this robot can only move).

Second, to generate the a posteriori estimate, the \texttt{ekfUpdate} function calls the 
\texttt{ekfCorrectionStep}. The \texttt{ekfCorrectionStep} in turn integrates all of the sensor 
data it is passed to create a new model for the robot's and the obstacles' states. It does this 
by stepping through the Extended Kalman Filter algorithm's correction step with each set of 
sensor data. For example, \texttt{ekfCorrectionStep} will call \texttt{kinectUpdate} and pass the 
data from the Kinect sensor to correct the positions of the obstacles.

>>>>

%---------------------------------
% Manually-included packages
\usepackage{amsmath}
\usepackage{graphicx}

@@

Once these measurements are collected, the \texttt{EKFSlammer} class is instantiated. This class 
represents the robot's predicted measurements by the Extended Kalman Filter. It also represents 
the EKF's entire algorithmic complexity. The \textit{a priori} and the \textit{a posteriori} estimation steps are 
performed through several of the \texttt{EKFSlammer}'s class methods.

\texttt{EKFSlammer} stores the robot's and environment's state $x_t$ in a \texttt{VectorXd}. The
perceived position and orientation of the robot, as well as the location of the obstacles in the map, 
can be expressed informally as 
\begin{equation*}
 x_t = \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
        \vec{s} \\
        \theta \\
        \vec{i}_1 \\
        \vec{i}_2 \\
        \vdots
        \end{IEEEeqnarraybox*}\right],
\end{equation*}
where $\vec{s}$ is the robot's location with respect to the Aruco Marker (the arbitrarily-defined
origin) and $\vec{i}_n$ is the location of the $i$\textsuperscript{th} obstacle. The vectors represented
in code for measurement updates are the Kinect measurement vector and the gyroscope measurement vector.
The Kinect senses all obstacles in the environment; therefore, its measurement vector for all $i$ obstacles 
is expressed as
\begin{equation*}
 z_{t,K} = \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           r_1 \\
           \theta_1 \\
           r_2 \\
           \theta_2 \\
           \vdots \\
           r_i \\
           \theta_i
           \end{IEEEeqnarraybox*}\right] + \vec{\epsilon_t},
\end{equation*}
and the gyroscope measurement vector can be expressed as 
\begin{equation*}
 z_{t,g} = \omega_t + \epsilon_t,
\end{equation*}
where $\omega_t$ is the angular velocity of the robot, and $\vec{\epsilon_t}$ and $\epsilon_t$ are the 
normally-distributed noise factors for each sensor.

@@

First, to generate the \textit{a priori} estimate, the \texttt{motionModelUpdate()} method is called by 
\texttt{ekfUpdate}. Its parameters are the timestep for the robot and its control parameters, in 
the form of a forward velocity and an angular velocity (i.e. the \texttt{controlIn} struct; see 
\texttt{Utils.h}). The \texttt{motionModelUpdate} will recalculate the estimated state of the 
robot, given the control input and given the known uncertainties of the robot's actuators 
(i.e. the robot's wheels, since this robot can only move).

The motion model update for the \textit{a priori} estimate is defined with the following relation, given
the robot's control sequence straight-line velocity $v_t$ and angular velocity $\omega_t$:
\begin{equation*}
\left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           x_{t+1} \\
           y_{t+1} \\
           \theta_{t+1}
           \end{IEEEeqnarraybox*}\right] = 
           \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           x_{t} \\
           y_{t} \\
           \theta_{t}
           \end{IEEEeqnarraybox*}\right] + 
           \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           -v_t/\omega_t \sin(\theta_t) + v_t/\omega_t \sin(\theta_t + \omega_t \Delta t)\\
           v_t/\omega_t \cos(\theta_t) - v_t/\omega_t\cos(\theta_t + \omega_t \Delta t)\\
           \omega_t \Delta t
           \end{IEEEeqnarraybox*}\right]
\end{equation*}
If covariance of the current state is $\Sigma_t$, then the Extended Kalman Filter approximates the 
covariance of the new \textit{a priori} state $\widehat{\Sigma_{t}}$ to be 
\begin{equation*}
 \widehat{\Sigma_t} = G_t \Sigma_t G_t^T + R_t,
\end{equation*}
where $G_t$ is the Jacobian of the robot's motion, and $R_t$ is a noise factor. Formally,
\begin{equation*}
G_t = \left[\begin{IEEEeqnarraybox*}[][c]{,c/c,}
            G^x_t & \textbf{0} \\
            \textbf{0} & I_{2N \times 2N}
           \end{IEEEeqnarraybox*}\right],
\end{equation*}
where $N$ is the number of obstacles (the quantity $2N$ above is because there are two coordinates for
each obstacle) and
\begin{equation*}
 G^x_t = \left[\begin{IEEEeqnarraybox*}[][c]{,c/c/c,}
            1\,   &  \, 0 \,  &  -v_t/\omega_t \cos(\theta_t) + v_t/\omega_t \sin(\theta_t + \omega_t \Delta t) \\
            0\,   &  \, 1 \,  &  -v_t/\omega_t \sin(\theta_t) + v_t/\omega_t \sin(\theta_t + \omega_t \Delta t) \\
            0\,   &  \, 0 \,  &   1
           \end{IEEEeqnarraybox*}\right].
\end{equation*}

Second, to generate the \textit{a posteriori} estimate, the \texttt{ekfUpdate} function calls the 
\texttt{ekfCorrectionStep}. The \texttt{ekfCorrectionStep} in turn integrates all of the sensor 
data it is passed to create a new model for the robot's and the obstacles' states. It does this 
by stepping through the Extended Kalman Filter algorithm's correction step with each set of 
sensor data. For example, \texttt{ekfCorrectionStep} will call \texttt{kinectUpdate} and pass the 
data from the Kinect sensor to correct the positions of the obstacles.

The measurement update must calculate certain values to integrate the sensor data into the estimated
state, such as the Kalman gain $K_t$:
\begin{equation*}
 K_t = \widehat{\Sigma_t} H_t^T (H_t \widehat{\Sigma_t} H_t^T + Q_t)^{-1},
\end{equation*}
where $H_t$ is the Jacobian of each predicted sensor measurement.

The Kalman gain is a weight for the updated state and covariance to depend on the predicted state 
verses the observed state. The updated state is
\begin{equation*}
 x_{t+1} = \hat{x_t} + K_t(z_t-h(\hat{x_t})),
\end{equation*}
and the updated covariance is 
\begin{equation*}
 \Sigma_{t+1} = (I - K_t H_t) \widehat{\Sigma_t}.
\end{equation*}
This \textit{a posteriori} correction step is performed for each set of sensor data to get an accurate
value for the mean and covariance of the new state.
